fdcoexist

### 2018-08-27 paper_simulations.Rmd
Plot linking R2 of CWM vs Env or trait variance to growth contribution added.

>>>>

```{r link_r2_cwm_trait_var}

all_trait_var$contrib2 <- as.numeric(gsub(".*R|A.*", "",
                                          all_trait_var$scenario))
all_trait_var$contrib1 <- 100 - all_trait_var$contrib2

# Plot
plot_grid(
    ggplot(mod_df[which(mod_df$env_width == "constant" &
                            mod_df$compet_status == "compet" &
                            mod_df$cwm_name == "trait2_cwm"), ],
           aes(as.factor(contrib2), adj.r.squared)) +
        geom_boxplot(aes(fill = cor_level)) +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(x = "Contribution of trait2 to growth (in %)",
             y = "R² of the relationship between\nCWM and environment"),
    ggplot(all_trait_var[which(all_trait_var$compet_status == "compet" &
                                   all_trait_var$env_width == "constant" &
                                   all_trait_var$trait_name == "trait2_var"), ],
           aes(as.factor(contrib2), trait_value)) +
        geom_boxplot(aes(fill = cor_level)) +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(x = "Contribution of trait2 to growth (in %)",
             y = "Variance of trait2 within the patch"),
    nrow = 2)
